---
title: "Replication code"
author: "Alexey Bessudnov"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

```

This is a replication code to reproduce the results in Bessudnov, A. \& Shcherbak, A. "Ethnic hierarchy in the Russian labour market: A field experiment".

# Install and attach packages

```{r}
library(tidyverse)
library(knitr)
library(survey)
library(srvyr)
library(stargazer)
```

# Name recognition survey (table 2)

```{r}
Names <- read.csv("SurveyPublic.csv")
Names <- Names %>%
        filter(loc != "abroad") %>%
        filter(ethnLabel != "Bashkir") %>%
        filter(ethnLabel != "Belarusian") %>%
        filter(ethnLabel != "Dagestani") %>%
        filter(ethnLabel != "Estonian") %>%
        filter(ethnLabel != "Kazakh") %>%
        filter(ethnLabel != "Kyrgyz") %>%
        filter(ethnLabel != "Moldovan")
Names %>%
        group_by(ethnLabel) %>%
        summarise(
                Correct = mean(correct, na.rm = TRUE) * 100,
                CorrectBroad = mean(correct.broad, na.rm = TRUE) * 100,
                NotRussian = mean(notRussian, na.rm = TRUE) * 100
        ) %>%
        arrange(desc(Correct)) %>%
        kable(col.names = c("Ethnic group", "% correct", "% broadly correct", "% not Russian"), digits = 0)
```

# Open the data from the experiment and recode variables

```{r}
Vacancies <- read_csv("VacanciesPublic.csv")

# Converting variables into factors 
Vacancies$RA <- factor(Vacancies$RA)
Vacancies$city <- factor(Vacancies$city, levels = c("Moscow", "St Petersburg", "Kazan", "Ufa"))
Vacancies$city2 <- factor(Vacancies$city2, levels = c("Moscow/St Petersburg", "Kazan/Ufa"))
Vacancies$occupation <- factor(Vacancies$occupation, levels = c("cook", "salesperson",
                                                                "sales manager", "programmer"))
Vacancies$gender <- factor(Vacancies$gender, levels = c("female", "male"))
Vacancies$ethnicity <- factor(Vacancies$ethnicity,
        levels = c("Russian", "Jewish", "Ukrainian",
        "German", "Lithuanian", "Latvian", "Georgian", "Armenian", "Tatar",
        "Bashkir", "Chechen", "Azeri", "Tajik", "Uzbek"))
Vacancies$ethnCollapsed <- factor(Vacancies$ethnCollapsed,
        levels = c("Russian", "Jewish", "Ukrainian", "German", "Latvian/Lithuanian",
                   "Tatar", "Tajik/Uzbek", "Chechen/Azeri",  "Armenian", "Georgian"))
Vacancies$ethnGroup2 <- factor(Vacancies$ethnGroup2,
        levels = c("European", "Southern"))
Vacancies$website <- factor(Vacancies$website)
Vacancies$candidateID <- factor(Vacancies$candidateID)

```

# Total number of job applications and contact rates (section 5.1)

```{r}

Vacancies %>%
        filter(ethnicity != "Bashkir") %>%
       nrow() %>%
        kable()

Vacancies %>%
        filter(ethnicity != "Bashkir") %>%
        summarise(
                overall = sum(response) / n(),
                onPhone = sum(phoneContact) / n(),
                onWebsite = sum(websiteContact) / n()
        ) %>%
        kable(digits = 2)
```

# Contact rates by ethnic group and location (table 4)


```{r}
descTable <- Vacancies %>%
        filter(ethnicity != "Bashkir") %>%
#         Using the srvyr package that lets us work with the survey functions
# within the tidyverse structures
        as_survey_design(ids = candidateID) %>%
        group_by(city2, ethnCollapsed) %>%
        summarise(
                # Total number of applications (with standard error that is unnecessary)
                n_app = survey_total(),
                # Total number of responses (with standard error that is unnecessary)
                n_response = survey_total(response),
                propContact = survey_mean(response, vartype = "ci")
        ) %>%
        as_tibble()

# odds of receiving response for Russians in Moscow/St Peterbsurg
oddsRusMSP <- descTable %>%
        filter(ethnCollapsed == "Russian" & city2 == "Moscow/St Petersburg") %>%
        summarise(
           odds =   n_response / (n_app - n_response)
        ) %>%
        as.numeric()
# odds of receiving response for Russians in Kazan/Ufa
oddsRusKU <- descTable %>%
        filter(ethnCollapsed == "Russian" & city2 == "Kazan/Ufa") %>%
        summarise(
           odds =   n_response / (n_app - n_response)
        ) %>%
        as.numeric()

# proportion response for Russians in Moscow/StPeterbsurg
propRusMSP <- descTable %>%
        filter(ethnCollapsed == "Russian" & city2 == "Moscow/St Petersburg") %>%
        select(propContact) %>%
        as.numeric()

# proportion response for Russians in Kazan/Ufa
propRusKU <- descTable %>%
        filter(ethnCollapsed == "Russian" & city2 == "Kazan/Ufa") %>%
        select(propContact) %>%
        as.numeric()

# Updating the table
descTable <- descTable %>%
        select(-c(n_response_se, n_app_se)) 
```

Moscow and St Petersburg

```{r}
# Moscow and St Petersburg
descTable %>%
        filter(city2 == "Moscow/St Petersburg") %>%
        mutate(oddsRus = oddsRusMSP) %>%
        mutate(propRus = propRusMSP) %>%
        mutate(cbkRatio = propRus / propContact) %>%
        mutate(or = (n_response / (n_app - n_response)) / oddsRus) %>%
        select(-c(propRus, oddsRus)) %>%
        arrange(desc(or)) %>%
        kable(digits = 2)
``` 

Kazan and Ufa

```{r}              
# Kazan and Ufa
descTable%>%
        filter(city2 == "Kazan/Ufa") %>%
        mutate(oddsRus = oddsRusKU) %>%
        mutate(propRus = propRusKU) %>%
        mutate(cbkRatio = propRus / propContact) %>%
        mutate(or = (n_response / (n_app - n_response)) / oddsRus) %>%
        select(-c(propRus, oddsRus)) %>%
        arrange(desc(or)) %>%
        kable(digits = 2)
               
```

n_app: the number of job applications sent;

n_response: the number of positive responses received;

propContact: proportion contacted (n_response / n_app);

propContact_low: lower bound of the 95% CI for prop_Contact;

propContact_upp: upper bound of the 95% CI for prop_Contact;

cbkRatio: calllback ratio (propRus / propContact);

or: odds ratio ((n_response / n_nonresponse) / (n_responseRus / n_nonresponseRus)).

# Contact rates by ethnic group and location: chart (figure 1)

```{r}
Vacancies %>%
        filter(ethnicity != "Bashkir") %>%
        as_survey_design(ids = candidateID) %>%
        group_by(city2, ethnCollapsed) %>%
        summarise(
                propContact = survey_mean(response, vartype = "ci")
        ) %>%
        arrange(desc(propContact)) %>%
        ggplot(aes(x = reorder(ethnCollapsed, propContact), y = propContact,
                        ymin = propContact_low, ymax = propContact_upp, linetype = city2)) +
        geom_point(position = position_dodge(width = 0.2), aes(shape = city2)) +
        geom_errorbar(position = position_dodge(width = 0.2), width = 0.1) +
        coord_flip() +
        ylab("Probability of contact") + 
        xlab("Ethnic group") +
        labs(shape="City") +
        scale_linetype_manual(name = "City",
                               values = 1:2) + 
        scale_shape_manual(name = "City",
                            values = 16:17) +
        theme(legend.position = "bottom") +
        theme(legend.title=element_blank())

```

# Linear probability models for contact (table 5)

```{r results = 'asis'}


# Moscow and St Petersburg
Vacancies.MSP <- Vacancies %>%
        filter(city2 == "Moscow/St Petersburg") %>%
        as_survey_design(ids = candidateID)
Vacancies.KU <- Vacancies %>%
        filter(city2 == "Kazan/Ufa") %>%
        as_survey_design(ids = candidateID)

# Estimating the models

m1 <- svyglm(response ~ ethnCollapsed + gender + occupation + city + website + RA, design = Vacancies.MSP)
m2 <- svyglm(response ~ ethnCollapsed + gender + occupation + city + website + RA, design = Vacancies.KU)

stargazer(m1, m2, type = "html", omit.stat = c("rsq", "adj.rsq", "f", "ser", "bic", "aic", "ll"), column.labels = c("Moscow/St Petersburg", "Kazan/Ufa"),
          omit = c("gender", "occupation", "city", "website", "RA", "Constant"),
          covariate.labels = c("Jewish", "Ukrainian", "German", "Latvian/Lithuanian",
                               "Tatar", "Tajik/Uzbek", "Azerbaijani/Chechen",
                               "Armenian", "Georgian"),
          digits = 2)

```

Linear probability models. All the models control for gender, occupation, city, website, and research assistant's name. Cluster-robust standard errors applied (clustered by applicant's name). Ethnic Russians are the reference group.

# Interaction between ethnicity and gender (table 6)

```{r results = 'asis'}

# Gender

mGender1 <- svyglm(response ~ ethnGroup2  * gender + occupation + city + website + RA, design = Vacancies.MSP)
mGender2 <- svyglm(response ~ ethnGroup2  * gender + occupation + city + website + RA, design = Vacancies.KU)

stargazer(mGender1, mGender2, type = "html", omit.stat = c("rsq", "adj.rsq", "f", "ser", "bic", "aic", "ll"), column.labels = c("Moscow/St Petersburg", "Kazan/Ufa"),
           omit = c("occupation", "city", "website", "RA", "Constant"),
           covariate.labels = c("Southern", "male", "Southern:male"),
           digits = 2)
```

# Probability of getting an explicit rejection (table 7)

```{r results = 'asis'}

# Subset those with response = 0 only
Rejected <- Vacancies %>%
  filter(response == 0)

# Setting survey objects
# Moscow and St Petersburg
Rejected.MSP <- Rejected %>%
        filter(city2 == "Moscow/St Petersburg") %>%
        as_survey_design(ids = candidateID)
Rejected.KU <- Rejected %>%
        filter(city2 == "Kazan/Ufa") %>%
        as_survey_design(ids = candidateID)

# Contact on the phone
mRejected1 <- svyglm(rejected ~ ethnCollapsed + website + gender + occupation  + city + RA, design = Rejected.MSP)
mRejected2 <- svyglm(rejected ~ ethnCollapsed + website + gender + occupation  + city + RA, design = Rejected.KU)


stargazer(mRejected1, mRejected2, type = "html", omit.stat = c("rsq", "adj.rsq", "f", "ser", "bic", "aic", "ll"), column.labels = c("Moscow/St Petersburg", "Kazan/Ufa"),
           omit = c("website", "gender", "occupation", "city", "RA", "Constant"),
          covariate.labels = c("Jewish", "Ukrainian", "German", "Latvian/Lithuanian",
                               "Tatar", "Tajik/Uzbek", "Azerbaijani/Chechen",
                               "Armenian", "Georgian"),
          digits = 2)

```

# Contact on the phone and on the websites (table 8)

```{r results = 'asis'}

# Subset to those with response = 1 only
Response <- Vacancies %>%
  filter(response == 1)

# Setting survey objects
# Moscow and St Petersburg
Response.MSP <- Response %>%
        filter(city2 == "Moscow/St Petersburg") %>%
        as_survey_design(ids = candidateID)
Response.KU <- Response %>%
        filter(city2 == "Kazan/Ufa") %>%
        as_survey_design(ids = candidateID)

# Contact on the phone
mPhone1 <- svyglm(phoneContact ~ ethnCollapsed + website + gender + occupation  + city + RA, design = Response.MSP)
mPhone2 <- svyglm(phoneContact ~ ethnCollapsed + website + gender + occupation  + city + RA, design = Response.KU)


stargazer(mPhone1, mPhone2, type = "html", omit.stat = c("rsq", "adj.rsq", "f", "ser", "bic", "aic", "ll"), column.labels = c("Moscow/St Petersburg", "Kazan/Ufa"),
           omit = c("website", "gender", "occupation", "city", "RA", "Constant"),
          covariate.labels = c("Jewish", "Ukrainian", "German", "Latvian/Lithuanian",
                               "Tatar", "Tajik/Uzbek", "Azerbaijani/Chechen",
                               "Armenian", "Georgian"),
          digits = 2)

```

# Ethnicity of the employers in Kazan and Ufa (Discussion)

```{r}

Vacancies %>%
        filter(!is.na(notRussianEmp)) %>%
        count(city, notRussianEmp) %>%
        group_by(city) %>%
        mutate(freq = n / sum(n)) %>%
        kable(digits = 2)
```

# Contact rates by ethnic group in four cities (Appendix)

```{r}

Vacancies %>%
        filter(ethnicity != "Bashkir") %>%
        as_survey_design(ids = candidateID) %>%
        group_by(city, ethnCollapsed) %>%
        summarise(
                propContact = survey_mean(response, vartype = "ci")
        ) %>%
        arrange(desc(propContact)) %>%
        ggplot(aes(x = reorder(ethnCollapsed, propContact), y = propContact,
                   ymin = propContact_low, ymax = propContact_upp, linetype = city)) +
        geom_point(position = position_dodge(width = 0.2), aes(shape = city)) +
        geom_errorbar(position = position_dodge(width = 0.2), width = 0.1) +
        coord_flip() +
        ylab("Probability of contact") + 
        xlab("Ethnic group") +
        labs(shape="City") +
        scale_linetype_manual(name = "City",
                              values = 1:4) + 
        scale_shape_manual(name = "City",
                           values = c(16:17, 0, 4)) +
        theme(legend.position = "bottom") +
        theme(legend.title=element_blank())

```

# Contact rates by ethnic group (combined) in four cities (Appendix)

```{r}

Vacancies %>%
        filter(ethnicity != "Bashkir") %>%
        as_survey_design(ids = candidateID) %>%
        group_by(city, ethnGroup2) %>%
        summarise(
                propContact = survey_mean(response, vartype = "ci")
        ) %>%
        arrange(desc(propContact)) %>%
        ggplot(aes(x = reorder(ethnGroup2, propContact), y = propContact,
                   ymin = propContact_low, ymax = propContact_upp, linetype = city)) +
        geom_point(position = position_dodge(width = 0.2), aes(shape = city)) +
        geom_errorbar(position = position_dodge(width = 0.2), width = 0.1) +
        coord_flip() +
        ylab("Probability of contact") + 
        xlab("Ethnic group") +
        labs(shape="City") +
        scale_linetype_manual(name = "City",
                              values = 1:4) + 
        scale_shape_manual(name = "City",
                           values = c(16:17,0,4)) +
        theme(legend.position = "bottom") +
        theme(legend.title=element_blank())

```

# Interaction between ethnicity and occupation (Appendix)

```{r results = 'asis'}

mOcc1 <- svyglm(response ~ ethnGroup2  * occupation + gender + city + website + RA, design = Vacancies.MSP)
mOcc2 <- svyglm(response ~ ethnGroup2  * occupation + gender + city + website + RA, design = Vacancies.KU)

stargazer(mOcc1, mOcc2, type = "html", omit.stat = c("rsq", "adj.rsq", "f", "ser", "bic", "aic", "ll"), column.labels = c("Moscow/St Petersburg", "Kazan/Ufa"),
           omit = c("gender", "city", "website", "RA", "Constant"),
covariate.labels = c("Southern", "salesperson", "sales manager",
                     "programmer", "Southern * salesperson", "Southern * sales manager", "Southern * programmer"),
            digits = 2)
```